The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-27 paper/ms.tex
typo
exofop

\subsubsection{Chemical Composition}
\label{chemical}
The chemical compositions for each star were measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families. This was done to asses the Galactic populations from which these stars are drawn. The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be considered drawn from the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge. These alone allow us to predict that theses stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\
{\bf $\alpha$ elements:}\\
\begin{figure*}
\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}

@@

We believe in open science, and have therefore made all substantive products of this research available to the interested reader. All code used to produce smear light curves is available under a GPL~v3 license at \url{github.com/benjaminpope/keplersmear}. All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main sequence stars as discussed in Sections~\ref{pulsators} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product. TRES spectra are available from \textcolor{red}{somewhere}, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.

>>>>

\subsubsection{Chemical Composition}
\label{chemical}
The chemical compositions for each star were measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families. This was done to asses the Galactic populations from which these stars are drawn. The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be considered drawn from the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge. These alone allow us to predict that these stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\
{\bf $\alpha$ elements:}\\
\begin{figure*}
\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}

@@

We believe in open science, and have therefore made all substantive products of this research available to the interested reader. All code used to produce smear light curves is available under a GPL~v3 license at \url{github.com/benjaminpope/keplersmear}. All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main sequence stars as discussed in Sections~\ref{pulsators} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product. TRES spectra will be made available from the ExoFOP-TESS website, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.
